### 2015-03-14 paper/paper.tex
..

%%%%%%%%%%%Bibliography%%%%%%%%%%%
%\newpage
\vspace*{0.5cm}
\setstretch{1} % Set line spacing to 1 for the bibliography.
\begin{thebibliography}{9}

	\bibitem[Acemoglu, Akcigit and Celik(2014)]{AAC2014} \textbf{Acemoglu, Daron, Ufuk Akcigit and Murat Alp Celik} (2014). ``Young, Restless and Creative: Openness to Disruption and Creative Innovations." NBER Working Paper No. 19894

	\bibitem[Arora, Belenzon and Patacconi(2015)]{ABP2015} \textbf{Arora, Ashish, Sharon Belenzon and Andrea Patacconi} (2015). ``Killing the Golden Goose? The Decline of Science in Corporate R\&D." \textit{NBER Working Paper No. 20902}.

@@

	\bibitem[Autor, Katz and Kearney(2008)]{AKK2008} \textbf{Autor, David H., Lawrence F. Katz and Melissa S. Kearney} (2008). ``Trends in US wage inequality: Revising the revisionists." \textit{The Review of Economics and Statistics}, 90(2): 300-323.

	\bibitem[Autor, Levy and Murnane(2003)]{ALM2003} \textbf{Autor, David H., Frank Levy and Richard J. Murnane} (2003). ``The Skill Content of Recent Technological Change: An Empirical Exploration." \textit{The Quarterly Journal of Economics}, 118(4): 1279-1333.

	\bibitem[Baker, Bloom and Davis(2011)]{BBD2013} \textbf{Baker, Scott R., Nicholas Bloom and Steven J. Davis} (2013). ``Measuring economic policy uncertainty." \textit{Chicago Booth research paper}, 13-02.

@@

		\bibitem[Brynjolfsson, McAfee and Spence(2014)]{BMS2014}\textbf{Brynjolfsson, Erik, Andrew McAfee and Michael Spence} (2014). ``New World Order. Labor, Capital, and Ideas in the New Power Law Economy." \textit{Foreign Affairs}, 93(4): 44-53.

	\bibitem[Ebenstein, Harrison, McMillan and Phillips(2014)] {EHMP2014} \textbf{Ebenstein, Avraham, Ann Harrison, Margret McMillan and Shannon Phillips} (2014). ``Estimating the Impact of Trade and Offshroing on American Workers Using the Current Population Surveys." \textit{Review of Economics and Statistics}, 96(4): 581-595.

@@

	\bibitem[Goos, Manning and Salomons(2014)]{GMS2014} \textbf{Goos, Maarten, Alan Manning and Anna Salomons} (2014). ``Explaining Job Polarization: Routine-Biased Technological Change and Offshoring." \textit{American Economic Review}, 104(8): 2509-2526.

@@

	\bibitem[Hall, Jaffe and Trajtenberg(2001)]{HJT2001} \textbf{Hall, Bronwyn H., Adam B. Jaffe and Manuel Trajtenberg} (2001). ``The NBER Patent Citation Data File: Lessons, Insights and Methodologial Tools". \textit{NBER Working Paper No. 8498}.

	\bibitem[Hansen, McMaho and Prat(2014)]{HMP2014} \textbf{Hansen, Stephen, Michael McMahon and Andrea Prat} (2014). ``Transparency and Deliberation within the FOMC:
a Computational Linguistics Approach". CEPR Discussion Paper 9994.

@@

	\bibitem[Hummels, Jørgensen, Munch and Xiang(2014)]{HJMX2014} \textbf{Hummels, David, Rasmus Jørgensen, Jakob Munch and Chong Xiang} (2014). ``The Wage Effects of Offshoring: Evidence from Danish Matched Worker-Firm Data." \textit{American Economic Review}, 104(6): 1597-1629.

@@

	\bibitem[Magerman, Van Looy and Song(2010)]{MVS2010} \textbf{Magerman, Tom, Bart Van Looy and Xiaoyan Song} (2010). ``Exploring the feasibility and accuracy of Latent Semantic Analysis based on text mining techniques to detect similarity between patent documents and scientific publication." \textit{Scientometrics}, 82(2): 289-306.

	\bibitem[Manning, Raghavan and Schütze(2009)]{MRS2009} \textbf{Manning, Christopher D., Prabhakar Raghavan and Hinrich Schütze} (2009). \textit{An Introduction to Information Retrieval.}  Cambridge University Press.

>>>>

%%%%%%%%%%%Bibliography%%%%%%%%%%%
\clearpage
\vspace*{0.5cm}
\setstretch{1} % Set line spacing to 1 for the bibliography.
\begin{thebibliography}{9}

	\bibitem[Acemoglu et al.(2014)]{AAC2014} \textbf{Acemoglu, Daron, Ufuk Akcigit and Murat Alp Celik} (2014). ``Young, Restless and Creative: Openness to Disruption and Creative Innovations." NBER Working Paper No. 19894

	\bibitem[Arora et al.(2015)]{ABP2015} \textbf{Arora, Ashish, Sharon Belenzon and Andrea Patacconi} (2015). ``Killing the Golden Goose? The Decline of Science in Corporate R\&D." \textit{NBER Working Paper No. 20902}.

@@

	\bibitem[Autor et al.(2008)]{AKK2008} \textbf{Autor, David H., Lawrence F. Katz and Melissa S. Kearney} (2008). ``Trends in US wage inequality: Revising the revisionists." \textit{The Review of Economics and Statistics}, 90(2): 300-323.

	\bibitem[Autor et al.(2003)]{ALM2003} \textbf{Autor, David H., Frank Levy and Richard J. Murnane} (2003). ``The Skill Content of Recent Technological Change: An Empirical Exploration." \textit{The Quarterly Journal of Economics}, 118(4): 1279-1333.

	\bibitem[Baker et al.(2011)]{BBD2013} \textbf{Baker, Scott R., Nicholas Bloom and Steven J. Davis} (2013). ``Measuring economic policy uncertainty." \textit{Chicago Booth research paper}, 13-02.

@@

		\bibitem[Brynjolfsson et al.(2014)]{BMS2014}\textbf{Brynjolfsson, Erik, Andrew McAfee and Michael Spence} (2014). ``New World Order. Labor, Capital, and Ideas in the New Power Law Economy." \textit{Foreign Affairs}, 93(4): 44-53.

	\bibitem[Ebenstein et al.(2014)] {EHMP2014} \textbf{Ebenstein, Avraham, Ann Harrison, Margret McMillan and Shannon Phillips} (2014). ``Estimating the Impact of Trade and Offshroing on American Workers Using the Current Population Surveys." \textit{Review of Economics and Statistics}, 96(4): 581-595.

@@

	\bibitem[Goos et al.(2014)]{GMS2014} \textbf{Goos, Maarten, Alan Manning and Anna Salomons} (2014). ``Explaining Job Polarization: Routine-Biased Technological Change and Offshoring." \textit{American Economic Review}, 104(8): 2509-2526.

@@

	\bibitem[Hall  et al.(2001)]{HJT2001} \textbf{Hall, Bronwyn H., Adam B. Jaffe and Manuel Trajtenberg} (2001). ``The NBER Patent Citation Data File: Lessons, Insights and Methodologial Tools". \textit{NBER Working Paper No. 8498}.

	\bibitem[Hansen et al.(2014)]{HMP2014} \textbf{Hansen, Stephen, Michael McMahon and Andrea Prat} (2014). ``Transparency and Deliberation within the FOMC:
a Computational Linguistics Approach". CEPR Discussion Paper 9994.

@@

	\bibitem[Hummels et al.(2014)]{HJMX2014} \textbf{Hummels, David, Rasmus Jørgensen, Jakob Munch and Chong Xiang} (2014). ``The Wage Effects of Offshoring: Evidence from Danish Matched Worker-Firm Data." \textit{American Economic Review}, 104(6): 1597-1629.

@@

	\bibitem[Magerman et al.(2010)]{MVS2010} \textbf{Magerman, Tom, Bart Van Looy and Xiaoyan Song} (2010). ``Exploring the feasibility and accuracy of Latent Semantic Analysis based on text mining techniques to detect similarity between patent documents and scientific publication." \textit{Scientometrics}, 82(2): 289-306.

	\bibitem[Manning et al.(2009)]{MRS2009} \textbf{Manning, Christopher D., Prabhakar Raghavan and Hinrich Schütze} (2009). \textit{An Introduction to Information Retrieval.}  Cambridge University Press.
